Stack Safety as a Security Property

### 2020-07-03 main.tex

But what {\em is} this stack safety of which we speak? A precise formal
definition is lacking in the literature, with the notion usually being
defined negatively: through examples of stack unsafety
\rb{usually though not always; as noted below there are other
  approaches}\bcp{Yes, we have to be very careful about this}. Two classical
examples of stack unsafety appear in Figure~\ref{fig:stackunsafety}.
\apt{is this gone?}
\leo{Goal: on the left, a bad read; on the right, a bad write.}
\leo{Do we also need an example of ROP/control flow for the new
  part?}\bcp{If it is not too complicated to explain, we should definitely
  put it
  here.  If it is complicated, we can just say in text that there are other
  sorts of attacks too, and that we deal with them, and give a forward
  pointer.}
Recently, a \leo{inspiring/awesome/something good}\bcp{Maybe just say that
  we are only aware of one, quite recent, attempt to do something better} work reasoned
about a stack safety enforcement mechanism using capabilities\leo{cite};
but even here, stack safety is defined with respect to an abstract
machine that ``satisfies stack safety by construction,'' begging
the question of what {\em is} the property that holds by construction?
\apt{Suggest to move first sentence of next para up to this one.}

@@

While integrity and confidentiality are relatively standard security
properties, the stack-safety setting raises an interesting additional
challenge:
the notion of who the attacker is shifts throught execution. Not only
does a caller need to be protected from its callee, but the callee
itself needs to be proteced from {\em its} callees.
We address this challenge by varying the access powers
of the attacker at call points, and demonstrate that our policy is
implementable by pre-existing monitoring mechanisms. \bcp{The two parts of
  the sentence are about two very different things.  The second deserves its
  own paragraph, IMO.}\apt{+1}

@@

%\leo{There needs to be some informal description
%  of the wbcf part here. Sean?}

In summary, we offer the following contributions\apt{is this up to date with current paper organization?}:
\begin{itemize}
\item \leo{More? Extensional}\bcp{We might need to invent a word for this---''quasi-extensional''?} formal characterizations of the
  intuitive concepts of local state encapsulation and
  well-bracketed control flow~(\Cref{sec:lse-and-wbcf}).  As evidence that this
  property is strong enough to capture the folk intuition, we show
  that the stack unsafe examples from the literature also fail our
  property~(\Cref{sec:disc}).\apt{Something about relation to StkTokens formalization?}
\item As evidence that the property is not too strong\apt{But we add the lazy version because the strict version \emph{is} too strong, in some sense.}, we show that it is
  realizible by
  a previously proposed micropolicy enforcement
  mechanism~(\Cref{sec:micropolicy}). \leo{And it says yes on a
    substantial body of code}. We also present a variation of the
  property + policy that is lazy, easier/more efficient to implement,
  and provably weaker (\Cref{sec:lazy}).
\item A provably stronger (inductive? step-by-step/stepwise) variant
  of this property tuned for testing/verification.  We test the whole
  thing with a cool framework. \bcp{Which section?}
\end{itemize}
Section~\ref{sec:relwork} discusses related work, and
Section~\ref{sec:future} sketches directions for future work.
%
We begin with a running example that we're going to keep coming back
to throughout the paper (Section~\ref{sec:running-example}) and some
technical preliminaries (Section~\ref{sec:prelim}).

@@

@@

\section{Background}
\label{sec:prelim}

@@

@@

Our properties and policies are parameterized by several types of
annotations describing features of a program. A {\em code map}
identifies some addresses as code and assigns each to a function. A
{\em call map} identifies addresses that complete a call sequence,
abstracting away from any concrete calling convention. Likewise a {\em
  return map} identifies addresses that complete a return sequence. An
{\em entry map} identifies valid entry points to a function.

@@

\section{Discussion}
\bcp{Make this a subsection?}
\label{sec:disc}

  \paragraph{Examples}

\bcp{Belongs with the running example:}
  \bcp{Illustrate the definition by using it to discuss a range of ``stack
    unsafety'' examples from the literature. }

@@

>>>>

But what {\em is} this stack safety of which we speak? A precise formal
definition is lacking in the literature, with the notion usually being
defined negatively: through examples of stack unsafety
\rb{usually though not always; as noted below there are other
  approaches}\bcp{Yes, we have to be very careful about this}.
\leo{Examples at a high level}
Recently, a \leo{inspiring/awesome/something good}\bcp{Maybe just say that
  we are only aware of one, quite recent, attempt to do something better} work reasoned
about a stack safety enforcement mechanism using capabilities\leo{cite};
but even here, stack safety is defined with respect to an abstract
machine that ``satisfies stack safety by construction,'' begging
the question of what {\em is} the property that holds by construction?
\apt{Suggest to move first sentence of next para up to this one.}

@@

While integrity and confidentiality are relatively standard security
properties, the stack-safety setting raises an interesting additional
challenge:
the notion of who the attacker is shifts throught execution. Not only
does a caller need to be protected from its callee, but the callee
itself needs to be proteced from {\em its} callees.
We address this challenge by varying the access powers
of the attacker at call points.

@@

 and demonstrate that our policy is
implementable by pre-existing monitoring mechanisms. \bcp{The two parts of
  the sentence are about two very different things.  The second deserves its
  own paragraph, IMO.}\apt{+1}
%\leo{There needs to be some informal description
%  of the wbcf part here. Sean?}

In summary, we offer the following contributions\apt{is this up to date with current paper organization?}:
\begin{itemize}
\item \leo{More? Extensional}\bcp{We might need to invent a word for
  this---''quasi-extensional''?} formal characterizations of the
  intuitive concepts of local state encapsulation and well-bracketed
  control flow~(\Cref{sec:lse-and-wbcf}). \leo{Make one sentence} examples from the literature also fail our
  property.\apt{Something about relation to StkTokens formalization?}
\item Case Study:
  \leo{Existing enforcement (Nick-eager). Satisfies Property.
  Satisfies even stronger property (provably).}
\item Pragmatically motivated refinement:
  \leo{Lazy enforcement mechanism (Nick-lazy).
    Plus a lazy variant of the property.}
%\item As evidence that the property is not too strong\apt{But we add the lazy version because the strict version \emph{is} too strong, in some sense.}, we show that it is
%  realizible by
%  a previously proposed micropolicy enforcement
%  mechanism~(\Cref{sec:micropolicy}). \leo{And it says yes on a
%    substantial body of code}. We also present a variation of the
%  property + policy that is lazy, easier/more efficient to implement,
%  and provably weaker (\Cref{sec:lazy}).
%\item A provably stronger (inductive? step-by-step/stepwise) variant
%  of this property tuned for testing/verification.  We test the whole
%  thing with a cool framework. \bcp{Which section?}
\end{itemize}
Section~\ref{sec:relwork} discusses related work, and
Section~\ref{sec:future} sketches directions for future work.
%
We begin with a running example that we're going to keep coming back
to throughout the paper (Section~\ref{sec:running-example}) and some
technical preliminaries (Section~\ref{sec:prelim}).

@@

\leo{TODO: Add citations of mitigation techniques}

@@

\paragraph*{Reusing call frames}

\leo{TODO}

\section{Machines, Traces, and Observations}
\label{sec:prelim}

@@

\leo{Policies of interest: null, micro, cherri, software-only}
\leo{TODO: Write down carefully}

@@

Our properties and policies are parameterized by several types of
annotations describing features of a program. A {\em code map}
\leo{TODO: function map}
identifies some addresses as code and assigns each to a function. A
{\em call map} identifies addresses that complete a call sequence,
abstracting away from any concrete calling convention. Likewise a {\em
  return map} identifies addresses that complete a return sequence. An
{\em entry map} identifies valid entry points to a function.

@@

@@

\section{Discussion}

\bcp{Make this a subsection?}
\label{sec:disc}
